Investigating Overfitting in Convolutional Neural Networks

### 2025-05-19 paper.tex
Got rid of chatgpt writing
fixed crash with \mathbf

    We trained \mathbf{x} convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
    parameters ranging from approximately 1 million to 50 million.

    For each model, we calculated:

    \[
        \Delta \text{Accuracy} = \text{Train Accuracy} - \text{Test Accuracy}
    \]

    We then analyzed the relationship between \( \Delta \text{Accuracy} \) and the model size.

>>>>

    We trained $\mathbf{x}$ convolutional models on the CIFAR-10 dataset, each with the same architecture (pictured below) but different numbers of
    parameters ranging from approximately 1 million to 50 million.
